\documentclass[letterpaper,10pt]{article}

\usepackage[T1]{fontenc}

\usepackage{fontawesome}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[colorlinks,pdftex]{hyperref}
\usepackage{fancyhdr}
\usepackage{multicol}
\usepackage{eurosym}
\usepackage{xcolor}
\usepackage{xfrac}
\usepackage{vwcol} 
\usepackage{adjustbox}
\definecolor{myBlue}{rgb}{0,0,0.55}


\hypersetup{
    urlcolor = {[rgb]{0,0,0}}
}

\newcommand\dunderline[3][-1pt]{{%
  \sbox0{#3}%
  \ooalign{\copy0\cr\rule[\dimexpr#1-#2\relax]{\wd0}{#2}}}}

\pagestyle{fancy}
\fancyhf{} 
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\usepackage{geometry}
\geometry{top=0.3cm, bottom=0.5cm, left=0.4cm, right=0.4cm}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-1pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2\vspace{-0.8pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{1.15pt}
  \small
  \item
    \begin{tabular*}{0.97\textwidth}{l @{\extracolsep{\fill}}r}
      \normalsize{\textbf{#1}}   & #2 \\
      \small{#3} & #4 \\
    \end{tabular*}
  \vspace{1.5pt}
}

\def\Plus{\texttt{+}}

% -------- ORIGINAL ------------

\newcommand{\resumeSubItem}[2]{
    \small{\resumeItem{#1}{#2}\vspace{-4pt}}
	}


\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-2pt}}


\newcommand{\resumeProjectListStart}{\begin{minipage}{0.97\textwidth} 
                                     \begin{itemize}[leftmargin=5mm]
                                     \vspace{3pt}}
\newcommand{\resumeProjectListEnd}{\end{itemize} 
                                   \end{minipage}}
\newcommand{\resumeProjectItem}[1]{
    \item\small{#1}
    }

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}


%----------HEADING-----------------
\begin{center}
  \begin{minipage}{0.97\textwidth}
      \begin{minipage}[c]{0.6\linewidth}
          \huge \textbf{Hugo \textsc{Jarkoff}}
          \\
          \emph{\large{Machine Learning Software Engineer (MSc.)}}
      \end{minipage}
      \hfill
      \begin{minipage}[c]{0.215\linewidth}
          \begin{tabular*}{\textwidth}{c@{\extracolsep{\fill}} l}
              \href{mailto:hugo.jarkoff@gmail.com}{\raisebox{-0.055\height}{\faEnvelope}} & \href{mailto:hugo.jarkoff@gmail.com}{\small{hugo.jarkoff@gmail.com}} \\
              \href{https://github.com/hugojarkoff}{\raisebox{-0.035\height}{\faGlobe}} & \href{https://hugojarkoff.github.io/}{\small{hugojarkoff.github.io}} \\
              \href{https://github.com/hugojarkoff}{\raisebox{-0.035\height}{\faGithub}} & \href{https://github.com/hugojarkoff}{\small{hugojarkoff}} \\
              \href{https://www.linkedin.com/in/hugojarkoff/}{\raisebox{-0.0925\height}{\faLinkedinSquare}} & \href{https://www.linkedin.com/in/hugojarkoff/}{\small{in/hugojarkoff}} \\
              {\raisebox{-0.0925\height}{\faHome}} & \small{Fontainebleau, France}
          \end{tabular*}
      \end{minipage}
  \end{minipage}
  \end{center}


%------------PROJET-----------------------
% \vspace{0.2mm}

\begin{center}
\begin{minipage}{0.95\textwidth}
    \centering
    \large \textbf{ML Software Engineer with 5\Plus \ years of experience in 
    designing, training and deploying models at scale; passionate by Distributed Systems and everything Computer Science related.}
\end{minipage}
\end{center}

\vspace{-4mm}

%-----------EXPERIENCE-----------------
\section{Experience}

\resumeSubHeadingListStart

\vspace{0.75mm}


\resumeSubheading{Addactis (formerly NamR, acquired in 2025)}{Paris, France}{ML/CV Software Engineer}{2024 - present}

High-impact contributions to aerial imagery and software products:
\resumeProjectListStart
\resumeProjectItem{Refactored the team's ML training framework, reducing time from data acquisition to production release by over 50\%.}
\resumeProjectItem{Redesigned the team's aerial imagery processing pipelines with serverless Cloud Run deployments, cutting legacy codebase size and reducing data integration time for ML workflows.}
\resumeProjectItem{Optimized the team's ML inference framework with PyTriton on serverless GPUs, reducing inference costs by enabling autoscaling to zero.}
\resumeProjectItem{Architectured, developed and deployed an AI Agent platform (FastAPI \Plus \ Pydantic-AI) integrating in existing SaaS insurance products.}
\resumeProjectListEnd

\resumeSubheading{Finegrain}{Paris, France}{ML/CV Software Engineer}{2024 (4 months)}

State-of-the-art generative model finetuning for image editing: 
\resumeProjectListStart
\resumeProjectItem{Finetuning of several pretrained models, including Segment Anything and Stable Diffusion, by using adapters (LoRAs, IP-Adapter) on target layers; lecture of scientific articles, keeping up with the latest advancements in the field.}
\resumeProjectItem{Contributions to the team's high-performance OSS micro-framework for foundation model adaptation (\href{https://github.com/finegrain-ai/refiners.}{Refiners}).}
\resumeProjectListEnd

\resumeSubheading{Invoxia}{Paris, France}{R\&D Machine Learning Engineer}{2021 -- 2024}

Led multiple end-to-end ML projects from research to deployment:
\resumeProjectListStart
\resumeProjectItem{Designed a CV-based signal processing model to estimate canine respiratory rate from accelerometer data; achieved 98.5\% accuracy (\href{https://www.biorxiv.org/content/10.1101/2023.06.09.544347v1}{preprint available}).}
\resumeProjectItem{Researched and adapted neural architectures (CNNs, Vision Transformers), focusing on model compression for embedded deployment.}
\resumeProjectItem{Deployed ML models to 10k\Plus \ production devices via Kubernetes and AWS SageMaker, with real-time monitoring (Grafana, Prometheus).}
\resumeProjectListEnd

% \resumeSubheading{Institut Louis Bachelier}{Paris, France}{End-of-Studies Internship}{2020 (6 months)}
% \resumeProjectListStart
% \resumeProjectItem{Researched online learning methods for training recurrent neural networks.}
% \resumeProjectListEnd

\resumeSubheading{Sopra Steria (for NavBlue - Airbus)}{Toulouse, France}{End-of-Studies Team Project}{2019 -- 2020}
\resumeProjectListStart
\resumeProjectItem{Developed an airport image segmentation and classification system using fully convolutional neural networks (UNet).}
\resumeProjectListEnd

% \resumeSubheading{Safran Aircraft Engines}{Villaroche, France}{Engineering Internship in Aero-Mechanical Optimization}{2018 (6 months)}
% \resumeProjectListStart
% \resumeProjectItem{Development of a new method for parameterizing engine blades based on a Bézier surfaces representation. Development and implementation of Python scripts for aero-mechanical optimization workflows.}
% \resumeProjectListEnd

\resumeSubHeadingListEnd


\vspace{-5mm}

%-----------EDUCATION-----------------
\section{Education}
\resumeSubHeadingListStart
\vspace{0.75mm}


\resumeSubheading{ISAE-SUPAERO}{Toulouse, France}{Engineering Degree (MSc.)}{2016 -- 2020}
\resumeProjectListStart
\resumeProjectItem{\textit{Major in Machine Learning}: Deep Learning (Computer Vision, NLP) - Reinforcement Learning - MLOps practices (databases architectures, Docker containerization, cloud computing).}
\resumeProjectItem{\textit{Minor in Advanced Mathematics}: Advanced statistics (non-parametric estimation, Bayesian statistics, stochastic algorithms) - High-performance and parallel computing - Modeling and analysis of multiphysics systems - Optimization.}
\resumeProjectListEnd

\resumeSubheading{Lycée Louis-le-Grand}{Paris, France}{Preparatory Classes}{2014 -- 2016}
\resumeProjectListStart
\resumeProjectItem{\textit{PCSI - PC*}: Mathematics - Physics - Chemistry - Computer Science.}
\resumeProjectListEnd

\resumeSubHeadingListEnd


\vspace{-4mm}

%-----------COMPETENCES TECHNIQUES + LANGUES -----------------
\begin{minipage}[t]{0.65\linewidth}
    \section{Technical Skills}
    \resumeSubHeadingListStart
    \resumeSubItem{Programming}{Python (OOP, design patterns, async APIs with FastAPI); Shell scripting; Familiar with C, C\Plus\Plus, Java, Lua (Neovim).}
    \resumeSubItem{Deep Learning}{PyTorch, TensorFlow, Keras.}
    \resumeSubItem{MLOps \& Infrastructure}{Docker, Kubernetes, Terraform, GitLab CI/CD, NVIDIA Triton, WandB, ClearML.}
    \resumeSubItem{Databases}{PostgreSQL, PostGIS.}
    \resumeSubItem{Cloud Platforms}{Google Cloud Platform (GCP), Amazon Web Services (AWS).}
    \resumeSubHeadingListEnd
    \end{minipage}
\hfill
\begin{minipage}[t]{0.3\linewidth}
    \section{Languages}
    \resumeSubHeadingListStart
    \resumeSubItem{French}{Native language.}
    \resumeSubItem{English}{Full professional proficiency. \\ \emph{TOEFL ITP}: 633/677.}
    \resumeSubHeadingListEnd
\end{minipage}


% \vspace{0.5mm}

%-----------PROJECTS-----------------
\section{Personal Projects and Diverse Interests}
\vspace{0.5mm}
\begin{minipage}[t]{0.9865\textwidth}
\resumeSubHeadingListStart
\resumeSubItem{Language Models Training}{RapGPT: Personal project consisting in training (from scratch) a Transformers-based language model to generate French Rap lyrics. 
Demo running on \href{https://huggingface.co/spaces/hugojarkoff/rapGPT}{HF}; weights also on \href{https://huggingface.co/hugojarkoff/rapGPT}{HF}; training code on \href{https://github.com/hugojarkoff/rapGPT}{GitHub}.}
  \resumeSubItem{Rock Climbing / Mountaineering}{Experienced climber and mountaineer (over 20 years of practice). Built a custom tool for measuring finger force (ESP32 soldered with deformation gauge, embedded with C software).}
\resumeSubHeadingListEnd
\end{minipage}


%-------------------------------------------
\end{document}
